Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-05-25 articles/formalism/sections/kernel_paintbrush.tex
made some clean up in the draft, changed revisit to comments for comments, added discussions on telescoping, updated telescoping behaviour of radial kernels notebook

The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.  However, unlike a complete ring, this filament is not a configuration with a definite parity.  Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.  A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.  A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.  We predict that it should be there in higher fidelity data.

The intuition from the real-space kernels holds also when we distort the shape of the filament.  If the filament were bent around into a circle, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.  The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.  The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.

>>>>

The non-zero $B$ result is somewhat surprising given that the polarization pattern is symmetric to both horizontal and vertical reflections through the filament center.  However, unlike a complete ring, this filament is not a configuration with a definite parity.  Because the scalar polarization descriptions are coordinate independent, the $E/B$ patterns do not depend on the orientation of the filament.  A filament inclined at $45^\circ$ will have a similar $E/B$ pattern, but different reflection symmetries.

%\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but no $B$-mode signal is above the noise.  We predict that it should be there in higher fidelity data.}
\revisit{A stacking analysis of Planck data \citep{2016A&A...586A.141P} sees $E>0$ along filaments (selected from intensity data), but claim no $B$-mode signal. We predict that a B-mode signal from filaments is present. A naive filament stacking analysis is only ideal for making E-mode detections. For detecting B-modes from filaments requires a more careful edge stacked filaments analysis. While its detectability from Planck requires more study, it should definitely be detectable in higher fidelity data.}

The intuition from the real-space kernels holds also when we distort the shape of the filament.  If the filament were bent around into a circle \comment{Not for an ellipse right? Maybe constant curvature argument is more general and more precise}, the positive and negative parts of the $B$ pattern will cancel, and we are left with a hoop of pure $E$ pattern.  The same general description holds for a spiral-shaped filament, which can can be viewed as distortion of the straight filament.  The filament is highlighted by positive $E>0$.  The $E$-pattern is more negative on the interior of a curve than on the exterior, and the concentric rings of filamentary structure make an increasingly negative $E$ value inside.  The $B$-pattern is again concentrated at the ends of the filament in an oriented pair of positive/negative fluctuations.
